### 2018-03-19 dissemination.publication/08da9685582866a0/paper.tex
added report and publication dummies

\documentclass[10pt,letterpaper,twocolumn]{article}

\usepackage[margin=2cm]{geometry}

%\special{papersize=8.3in,11.7in} % A4

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\usepackage{multicol}
%\usepackage{ifpdf}
%\usepackage{cite}
\usepackage{graphicx}
\usepackage{array}
%\usepackage{caption}
\usepackage{subfig}
%\usepackage{subfigure}
%\usepackage{fixltx2e}
\usepackage{algorithm,algorithmic}
\usepackage{color}
%\usepackage[hyphens]{url}
\usepackage{url}
\usepackage{hyperref}
\usepackage{listings}
\usepackage[none]{hyphenat}

\newenvironment{packed_itemize}{
\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{itemize}}

\renewcommand{\floatpagefraction}{.8}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title{}

\author{Nikolay Chunosov$^{1,2}$, Flavio Vella$^{1}$, Anton Lokhmotov$^{1}$, Grigori Fursin$^{1,3}$ \\
\\
$^1$~dividiti, UK ; $^2$~Xored, Russia ; $^3$~cTuning foundation, France\\
}

\date{March, 2018}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\maketitle

\begin{abstract}
 \input{paper_abstract}
\end{abstract}

{\bf Keywords:}
{\it\small 
 \input{keywords}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%CK_INTERACTIVE_START

%CK_ABSTRACT={paper_abstract.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction} % Has to be here (for interactive report!)
\label{introduction} % Has to be here (for interactive report!)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgments}
\label{sec:ack}

%CK_IMG={http://cknowledge.org/images/logo-dividiti2.png ; http://dividiti.com}
%CK_IMG={http://cknowledge.org/images/CTuning_foundation_logo2.png ; http://cTuning.org}

%CK_TEX={appendix1.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{abbrv}
\bibliography{paper}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix

\clearpage
\newpage
\pagebreak

\input{appendix1.tex}

\end{document}

### 2018-03-19 dissemination.publication/08da9685582866a0/_clean.sh

@@ -1,0 +1,13 @@
+#!/bin/bash
+
+echo "Cleaning..."
+
+rm -f paper.aux 
+rm -f paper.bbl
+rm -f paper.blg
+rm -f paper.dvi
+rm -f paper.log
+rm -f paper.out
+rm -f paper.pdf
+rm -f *.xcp
+rm -f *.out

### 2018-03-19 dissemination.publication/08da9685582866a0/_compile.sh

@@ -1,0 +1,14 @@
+#!/bin/bash
+source ./_clean.sh
+
+echo "Compiling article ..."
+
+pdflatex paper
+
+bibtex paper
+
+pdflatex paper
+pdflatex paper
+
+echo "Launching..."
+evince paper.pdf

### 2018-03-19 report/08da9685582866a0/generate.sh

@@ -1,0 +1,1 @@
+ck convert_to_live_ck_report dissemination.publication:08da9685582866a0 --output=interactive-ck-article.html

### 2018-03-19 report/08da9685582866a0/view.sh

@@ -1,0 +1,1 @@
+ck browser ^

### 2018-03-19 script/mobilenets-armcl-opencl/benchmark-add-dimensions.py

@@ -41,11 +41,10 @@ def do(i):
         dd['meta']['platform_species']='embedded' # embedded vs server (maybe other classifications such as edge)
 
         dd['meta']['platform_peak_power']=4.5 #Watts
-
         dd['meta']['platform_price']=239 # $
         dd['meta']['platform_price_date']='20170425' # date
 
-        dd['meta']['artifact']='' # date
+        dd['meta']['artifact']='08da9685582866a0' # artifact description
 
         # Updating entry
         r=ck.access({'action':'update',
@@ -76,8 +75,8 @@ def do(i):
 
                if mult==0.25: size=1990786
                elif mult==0.5: size=5459810
-               elif mult=0.75: size=10498594
-               elif mult=1.0: size=17106694
+               elif mult==0.75: size=10498594
+               elif mult==1.0: size=17106694
                else:
                   return {'return':1, 'error':'unknown width multiplier "'+str(mult)+'"'}
 

### 2018-03-20 script/mobilenets-armcl-opencl/benchmark-add-dimensions.py
added 3 dimensions (CPU freq, GPU freq, precision)

@@ -7,6 +7,7 @@ def do(i):
     # List performance entries
     r=ck.access({'action':'search',
                  'module_uoa':'experiment',
+#                 'repo_uoa':'ck-request-asplos18-results'})
                  'data_uoa':'mobilenets-performance-*'})
     if r['return']>0: return r
     lst=r['lst']
@@ -46,6 +47,8 @@ def do(i):
 
         dd['meta']['artifact']='08da9685582866a0' # artifact description
 
+        dd['meta']['model_precision']='fp32'
+
         # Updating entry
         r=ck.access({'action':'update',
                      'module_uoa':'experiment',
@@ -59,9 +62,13 @@ def do(i):
         if r['return']>0: return r
 
         # Checking points to aggregate
+        os.chdir(path)
         dperf=os.listdir(path)
         for f in dperf:
-            if f.endswith('.flat.json'):
+            if f.endswith('.cache.json'):
+               os.system('git rm -f '+f)
+
+            elif f.endswith('.flat.json'):
                ck.out(' * '+f)
 
                # Load performance file 
@@ -81,6 +88,9 @@ def do(i):
                   return {'return':1, 'error':'unknown width multiplier "'+str(mult)+'"'}
 
                d['##features#model_size#min']=size
+
+               d['##features#cpu_freq#min']='807'
+               d['##features#gpu_freq#min']=''
 
                # Save updated dict
                r=ck.save_json_to_file({'json_file':p1, 'dict':d, 'sort_keys':'yes'})

### 2018-03-21 program/mobilenets-armcl-opencl/mobilenets.cpp
store batches as i8

@@ -25,6 +25,7 @@
 #include "benchmark.h"
 
 #include "arm_compute/runtime/CL/CLTensor.h"
+#include "utils/Utils.h"
 
 class CKNumPyInputLoader : public ITensorAccessor {
 public:
@@ -43,8 +44,9 @@ public:
     
     s.measure_begin();
 
-    NumPyBinLoader accessor(batch_file);
-    accessor.access_tensor(tensor);
+    copy_int8_numpy_to_tensor(batch_file, tensor);
+    //NumPyBinLoader accessor(batch_file);
+    //accessor.access_tensor(tensor);
 
     auto t = s.measure_end_load_images();
     cout << "Loaded in " << t << " s\n";
@@ -52,6 +54,62 @@ public:
     // Start batch timer after data was loaded
     s.measure_begin();
     return true;
+  }
+
+private:
+  void copy_int8_numpy_to_tensor(const string& file_name, ITensor &tensor) {
+    // Open file
+    ifstream stream(file_name, ios::in | ios::binary);
+    if (!stream.good())
+      raise_error(file_name, "Unable to open file");
+    string header = npy::read_header(stream);
+
+    // Parse header
+    string typestr;
+    bool fortran_order = false;
+    vector<unsigned long> shape;
+    npy::parse_header(header, typestr, fortran_order, shape);
+
+    // Check if the typestring matches the given one
+    if (typestr != arm_compute::utils::get_typestring(DataType::U8))
+      raise_error(file_name, "Typestrings mismatch");
+
+    // Reverse vector in case of non fortran order
+    if(!fortran_order)
+      reverse(shape.begin(), shape.end());
+
+    // Correct dimensions (Needs to match TensorShape dimension corrections)
+    const TensorShape tensor_shape = tensor.info()->tensor_shape();
+    if(shape.size() != tensor_shape.num_dimensions())
+      for(int i = static_cast<int>(shape.size()) - 1; i > 0; --i)
+        if(shape[i] == 1)
+          shape.pop_back();
+        else
+          break;
+
+    // Validate tensor ranks and shapes
+    if (shape.size() != tensor_shape.num_dimensions())
+      raise_error(file_name, "Tensor ranks mismatch");
+    for(size_t i = 0; i < shape.size(); ++i)
+      if (tensor_shape[i] != shape[i])
+        raise_error(file_name, "Tensor dimensions mismatch");
+
[…]

### 2018-03-21 program/mobilenets-armcl-opencl/preprocess.py

@@ -92,18 +92,10 @@ def ck_preprocess(i):
       offset_h = (img.shape[1] - new_h)/2
       img = img[offset_w:new_w+offset_w, offset_h:new_h+offset_h, :]
 
-      # Convert to float and normalize
-      img = img.astype(np.float32)
-      img = img / 255.0
-
       # Zoom to target size
       zoom_w = float(IMAGE_SIZE)/float(img.shape[0])
       zoom_h = float(IMAGE_SIZE)/float(img.shape[1])
       img = zoom(img, [zoom_w, zoom_h, 1])
-
-      # Shift and scale
-      img = img - 0.5
-      img = img * 2
 
       # Each image is a batch in NCHW format
       img = img.transpose(2, 0, 1)

### 2018-03-21 program/mobilenets-armcl-opencl/preprocess.py
cache batches locally

@@ -25,19 +25,18 @@ def ck_preprocess(i):
   def dep_env(dep, var): return i['deps'][dep]['dict']['env'][var]
 
   # Init variables from environment
-  MODEL_DIR = dep_env('weights', 'CK_ENV_MOBILENET')
   BATCH_COUNT = int(my_env('CK_BATCH_COUNT'))
   BATCH_SIZE = int(my_env('CK_BATCH_SIZE'))
   IMAGES_COUNT = BATCH_COUNT * BATCH_SIZE
   SKIP_IMAGES = int(my_env('CK_SKIP_IMAGES'))
-  IMAGE_LIST = os.path.join(MODEL_DIR, my_env('CK_IMG_LIST'))
   IMAGE_DIR = dep_env('imagenet-val', 'CK_ENV_DATASET_IMAGENET_VAL')
   IMAGE_SIZE = int(dep_env('weights', 'CK_ENV_MOBILENET_RESOLUTION'))
-  BATCHES_DIR = os.path.join(MODEL_DIR, my_env('CK_BATCHES_DIR'))
-  BATCH_LIST = os.path.join(MODEL_DIR, my_env('CK_BATCH_LIST'))
+  MODE_SUFFIX = '-{}-{}-{}'.format(IMAGE_SIZE, BATCH_SIZE, BATCH_COUNT)
+  IMAGE_LIST = my_env('CK_IMG_LIST') + MODE_SUFFIX + '.txt'
+  BATCHES_DIR = my_env('CK_BATCHES_DIR') + MODE_SUFFIX
+  BATCH_LIST = my_env('CK_BATCH_LIST') + MODE_SUFFIX + '.txt'
   RESULTS_DIR = my_env('CK_RESULTS_DIR')
   PREPARE_ALWAYS = my_env('CK_PREPARE_ALWAYS')
-  PREPARED_INFO_FILE = os.path.join(MODEL_DIR, 'prepared_info.json')
 
   def prepare_batches():
     print('Prepare images...')
@@ -114,13 +113,6 @@ def ck_preprocess(i):
       for img in dst_images:
         f.write('{}\n'.format(img))
 
-    info = {}
-    info['resolution'] = IMAGE_SIZE
-    info['batch_count'] = BATCH_COUNT
-    with open(PREPARED_INFO_FILE, 'w') as f:
-      json.dump(info, f, indent=2, sort_keys=True)
-
-
   # Prepare results directory
   recreate_dir(RESULTS_DIR)
 
[…]

### 2018-03-21 program/mobilenets-armcl-opencl/mobilenets.cpp
comment removed

@@ -45,8 +45,6 @@ public:
     s.measure_begin();
 
     copy_int8_numpy_to_tensor(batch_file, tensor);
-    //NumPyBinLoader accessor(batch_file);
-    //accessor.access_tensor(tensor);
 
     auto t = s.measure_end_load_images();
     cout << "Loaded in " << t << " s\n";

### 2018-03-22 program/mobilenets-armcl-opencl/benchmark.cpp
check if image has alpha-channel

@@ -65,6 +65,7 @@ void finish_test() {
 }
 
 int run_test() {
+    ofstream err_log("test_errors.log", ios::trunc);
     try
     {
         session().init();
@@ -75,12 +76,18 @@ int run_test() {
     }
     catch (cl::Error &err)
     {
-        std::cerr << "\nERROR: " << err.what() << " (" << err.err() << ")" << std::endl;
+        ostringstream msg;
+        msg << "\nERROR: " << err.what() << " (" << err.err() << ")";
+        cerr << msg.str() << endl;
+        err_log << msg.str() << endl;
         return EXIT_FAILURE;
     }
     catch (std::runtime_error &err)
     {
-        std::cerr << "\nERROR: " << err.what() << " " << (errno ? strerror(errno) : "") << std::endl;
+        ostringstream msg;
+        msg << "\nERROR: " << err.what() << " " << (errno ? strerror(errno) : "");
+        cerr << msg.str() << endl;
+        err_log << msg.str() << endl;
         return EXIT_FAILURE;
     }
 }

### 2018-03-22 program/mobilenets-armcl-opencl/preprocess.py

@@ -80,6 +80,9 @@ def ck_preprocess(i):
       # check if grayscale and convert to RGB
       if len(img.shape) == 2:
         img = np.dstack((img,img,img))
+      # drop alpha-channel if present
+      if img.shape[2] > 3:
+        img = img[:,:,:3]
 
       # The same image preprocessing steps are used for MobileNet as for Inception:
       # https://github.com/tensorflow/models/blob/master/research/slim/preprocessing/inception_preprocessing.py

### 2018-03-22 script/mobilenets-armcl-opencl/benchmark.py
Append 'armcl-opencl' to record UOA.

@@ -229,7 +229,7 @@ def do(i, arg):
             alpha = float(r['dict']['env']['CK_ENV_MOBILENET_MULTIPLIER'])
             rho = int(r['dict']['env']['CK_ENV_MOBILENET_RESOLUTION'])
             record_repo='local'
-            record_uoa='mobilenets-'+experiment_type+'-'+str(rho)+'-'+str(alpha)+'-'+lib_tags
+            record_uoa='mobilenets-'+experiment_type+'-'+str(rho)+'-'+str(alpha)+'-armcl-opencl-'+lib_tags
 
             # Prepare pipeline.
             ck.out('---------------------------------------------------------------------------------------')

### 2018-05-31 dissemination.publication/08da9685582866a0/_clean.sh
clean up

@@ -1,13 +1,3 @@
 #!/bin/bash
 
-echo "Cleaning..."
-
-rm -f paper.aux 
-rm -f paper.bbl
-rm -f paper.blg
-rm -f paper.dvi
-rm -f paper.log
-rm -f paper.out
-rm -f paper.pdf
-rm -f *.xcp
-rm -f *.out
+rm -f *.aux *.dvi *.log *.pdf *.blg *.bbl *.xcp *.out *.cut

### 2018-05-31 dissemination.publication/08da9685582866a0/_compile.sh

@@ -1,4 +1,5 @@
 #!/bin/bash
+
 source ./_clean.sh
 
 echo "Compiling article ..."

### 2018-05-31 dissemination.publication/08da9685582866a0/paper.tex
ReadMe clean up and paper sources

@@
-\documentclass[10pt,letterpaper,twocolumn]{article}
+\documentclass[sigplan]{acmart}
 
-\usepackage[margin=2cm]{geometry}
+\usepackage{booktabs} % For formal tables
 
-%\special{papersize=8.3in,11.7in} % A4
+% Copyright
+%\setcopyright{none}
+%\setcopyright{acmcopyright}
+%\setcopyright{acmlicensed}
+\setcopyright{rightsretained}
+%\setcopyright{usgov}
+%\setcopyright{usgovmixed}
+%\setcopyright{cagov}
+%\setcopyright{cagovmixed}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\usepackage{multicol}
-%\usepackage{ifpdf}
-%\usepackage{cite}
+\usepackage{color}
+\usepackage{amssymb,amsmath}
 \usepackage{graphicx}
-\usepackage{array}
-%\usepackage{caption}
-\usepackage{subfig}
-%\usepackage{subfigure}
-%\usepackage{fixltx2e}
-\usepackage{algorithm,algorithmic}
-\usepackage{color}
-%\usepackage[hyphens]{url}
+\usepackage{wrapfig}
+\usepackage{epsfig}
+\usepackage[normalem]{ulem}
 \usepackage{url}
 \usepackage{hyperref}
+\usepackage{color}
+\usepackage{array}
+\usepackage{subfig}
+\usepackage{algorithm,algorithmic}
 \usepackage{listings}
-\usepackage[none]{hyphenat}
+%\usepackage[none]{hyphenat}
 
@@
 
-\renewcommand{\floatpagefraction}{.8}%
+% DOI
+\acmDOI{10.1145/3229762.3229767}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% ISBN
+\acmISBN{}
+
+%Conference
+\acmConference[ReQuEST at ASPLOS'18]{1st ACM SIGARCH Reproducible Quality-Efficient Systems Tournament and Workshop to Co-design Pareto-efficient Deep Learning}{March 2018}{Williamsburg, VA, USA}
+\acmYear{2018}
+\copyrightyear{2018}
+
+%\acmPrice{15.00}
+
+%\acmBadgeL[http://ctuning.org/ae/ppopp2016.html]{ae-logo}
+%\acmBadgeR[http://ctuning.org/ae/ppopp2016.html]{ae-logo}
 
@@
 
-\title{}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\title{Multi-objective autotuning of MobileNets\\ across the full software/hardware stack}
 
-\author{Nikolay Chunosov$^{1,2}$, Flavio Vella$^{1}$, Anton Lokhmotov$^{1}$, Grigori Fursin$^{1,3}$ \\
-\\
-$^1$~dividiti, UK ; $^2$~Xored, Russia ; $^3$~cTuning foundation, France\\
+%\titlenote{Produces the permission block, and
+%  copyright information}
+
+%\subtitle{Extended Abstract}
+
+%\subtitlenote{The full version of the author's guide is available as
+%  \texttt{acmart.pdf} document}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\author{Anton Lokhmotov}
+%\authornote{}
+\affiliation{%
+  \institution{dividiti}
 }
+\email{anton@dividiti.com}
 
-\date{March, 2018}
+\author{Nikolay Chunosov}
+\affiliation{%
+  \institution{Xored and dividiti}
+}
+\email{nikolay.chunosov@xored.com}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\author{Flavio Vella}
+%\authornote{}
+\affiliation{%
+  \institution{dividiti}
+}
+\email{flavio@dividiti.com}
 
-\maketitle
+\author{Grigori Fursin}
+\affiliation{%
+  \institution{dividiti and cTuning foundation}
+}
+\email{Grigori.Fursin@cTuning.org}
 
+\renewcommand{\shortauthors}{}
+\renewcommand{\shorttitle}{}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{abstract}
@@
 
-{\bf Keywords:}
-{\it\small 
- \input{keywords}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% The code below should be generated by the tool at
+% http://dl.acm.org/ccs.cfm
+% Please copy and paste the code instead of the example below.
+%
+
+%\begin{CCSXML}
+%\end{CCSXML}
+
+%\ccsdesc[500]{Computer systems organization~Embedded systems}
+%\ccsdesc[300]{Computer systems organization~Redundancy}
+%\ccsdesc{Computer systems organization~Robotics}
+%\ccsdesc[100]{Networks~Network reliability}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\keywords{\small MobileNets, Collective Knowledge, performance, accuracy,
+system co-design, reproducible experimentation, customizable workflows,
+autotuning, crowdtuning, live scoreboard}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\maketitle
+
+%===============================================================================
+\section{Introduction}
+\label{sec:intro}
+%===============================================================================
+
+MobileNets~\cite{Howard:MobileNets-v1} is a family of efficient convolutional
+neural network (CNN) models for mobile and embedded platforms.
+%
+In theory, using $3 \times 3$ depthwise separable convolutions results in
+8--9 times fewer operations than using standard $3 \times 3$ convolutions at a
+small loss of accuracy.
+%
+In practice, the execution time of a model depends on many factors, not
+just on the number of operations.
+
+We study performance (execution time and accuracy) trade-offs on two embedded
+development platforms (Table~\ref{tab:platforms}).
+%
+We use TensorFlow~\cite{tensorflow2015-whitepaper} on run MobileNets on the
+CPU, and the Arm Compute Library~\cite{arm-compute-library} (ArmCL) to run
+MobileNets on the GPU.
+%
+We use the same set of weights in all experiments (converted into
+the ArmCL format for GPU experiments).\footnote{Google released this set of
+weights on 14 June 2017. They subsequently released another set on 22 February
+2018. Both sets are available as Collective Knowledge components.}
+
+As we have contributed to the ArmCL optimizations for the latest Bifrost GPU
+architecture (Mali-G71), we evaluate their effectiveness on the HiKey platform
+over several public releases.
+%
+We also evaluate MobileNets on the Firefly platform with the previous Midgard
+GPU architecture (Mali-T860).
+
+To perform experiments across the many combinations of models, libraries, data
+sets and hardware, we use a Collective Knowledge workflow for
+autotuning~\cite{cm:29db2248aba45e59:c4b24bff57f4ad07}.
+%
+We make all the workflow components (models, programs, scripts, etc.) publicly
+available under the permissive Collective Knowledge license to encourage
+further exploration by the community in the spirit of the ACM ReQuEST
+tournaments~(Figure~\ref{fig:ck-request-concept}).
+
+%-------------------------------------------------------------------------------
+% Table 1.
+%-------------------------------------------------------------------------------
+\begin{table}
+\centering
+  \begin{tabular}{ll}
+  \toprule
+  \multicolumn{2}{c}{{\bf Linaro HiKey960 (``HiKey'')}}\\
+  \midrule
+  % https://www.96boards.org/product/hikey960/
+  System-on-chip      & HiSilicon Kirin960                      \\
+  CPU 0 (``LITTLE'')  & Arm Cortex-A53, 4 cores, $\le$ 1844 MHz \\
+  CPU 1 (``big'')     & Arm Cortex-A73, 4 cores, $\le$ 2362 MHz \\
+  GPU                 & Arm Mali-G71,   8 cores, $\le$ 1037 MHz \\
+  OpenCL              & Specification: 2.0; driver: 6.0         \\
+  RAM                 & 3 GiB                                   \\
+  \midrule
+  % http://en.t-firefly.com/product/rk3399.html
+  \multicolumn{2}{c}{{\bf T-Firefly RK3399 (``Firefly'')}}\\
+  \midrule
+  System-on-chip      & Rockchip RK3399                         \\
+  CPU 0 (``LITTLE'')  & Arm Cortex-A53, 4 cores, $\le$ 1416 MHz \\
+  CPU 1 (``big'')     & Arm Cortex-A72, 2 cores, $\le$ 1800 MHz \\
+  GPU                 & Arm Mali-T860,  4 cores, $\le$  800 MHz \\
+  OpenCL              & Specification: 1.2; driver: 13.0        \\
+  RAM                 & 4 GiB                                   \\
+  \bottomrule
+  \end{tabular}
+\caption{\label{tab:platforms}Experimental platforms.}
+\end{table}
+
+%-------------------------------------------------------------------------------
+%Figure 1.
+%-------------------------------------------------------------------------------
+\begin{figure*}[htb]
+% 
+  \centering
+%
+  \includegraphics[width=0.9\textwidth]{figures/ck-request-concept-cropped.pdf}
+%  
+  \caption{The Reproducible Quality-Efficiency Systems Tournaments
+(ReQuEST)~\cite{cm:29db2248aba45e59:0c7348dfbadd5b95} invite the
+interdisciplinary community to decompose the complex software/hardware
+benchmarking, optimization and co-design process into customizable workflows
+with reusable components, and collaboratively explore Pareto-efficient
+solutions in terms of speed, accuracy, energy, costs and other extensible
+metrics across diverse models, data sets, frameworks, libraries and platforms.}
+%
+  \label{fig:ck-request-concept}
+%
+\end{figure*}
+
+%===============================================================================
+\section{Experimental evaluation}
+\label{sec:evaluation}
+%===============================================================================
+
+\subsection{Parameter space}
+
+The MobileNets family offers two tunable parameters to trade off performance
+and accuracy: the input image resolution and the channel
+multiplier~\cite{Howard:MobileNets-v1}.
+
+Additionally, we study the effectiveness of library optimizations over several
+ArmCL variants for two convolution methods: {\em direct convolution} computes a
+weighted sum of input values ``ab initio''; {\em GEMM-based convolution} uses
+an ``image-to-column'' transformation of input values to reduce computation to
+a typically highly-optimized generic matrix-matrix multiplication routine
+(GEMM).
+
+\subsection{ArmCL Bifrost optimizations}
+
+Our optimizations for the Bifrost GPU architecture first appeared in the v17.12
+release of ArmCL.
+%
+These included writing new OpenCL kernels for most important CNN operators,
+restructuring kernels to expose more parallelism and improve locality (e.g.\
+kernel fusion), and introducing mechanisms for adaptively selecting the optimal
+workgroup size for the given tensor shape.
+
+Unfortunately, our optimizations were mostly disabled in v17.12 due to an issue,
+which got fixed in v18.01.
+%
+As the previous v17.10 release did not support depthwise convolutions, running
+MobileNets with v17.12 should give a good approximation of how the models would
+perform without our optimizations.
+
+Following the v18.01 release, Arm focused on improving the performance of
+GEMM-based convolutions, while we independently developed a new direct $1
+\times 1$ convolution kernel. 
+%
+We integrated this kernel into a fork of v18.03.
+%
+We refer to this fork as ``dv/dt'' in what follows.
+
+\subsection{Execution time vs.\ top 1 accuracy on HiKey}
+
+Figure~\ref{fig:50000} plots the execution time vs.\ top 1 accuracy over the
+full ImageNet validation set (50,000 images) on the HiKey platform with the
+following encoding:
+
+% https://github.com/ARM-software/ComputeLibrary/pull/432
+
+\begin{itemize}
+
+  \item The colour of a marker denotes the execution engine: TensorFlow on the CPU or the ArmCL on the GPU.
+
+  \item The size of a marker is proportional to the input image resolution: $224$ (the largest), $192$, $160$, $128$ (the smallest).
+
+  \item The shape of a marker denotes both the channel multiplier and the convolution method:
+  \begin{itemize}
+    \item Direct convolution: $1.00$ - pentagon, $0.75$ - square, $0.50$ - triangle-up, $0.25$ - circle.
+    \item GEMM-based convolution: $1.00$ - star, $0.75$ - diamond, $0.50$ - triangle-down, $0.25$ - octagon.\footnote{%
+      Roughly speaking, a shape has $N$ corners for the channel multiplier of $(N-1)/4$:
+      \begin{itemize}
+        \item 5 corners for the channel multiplier of $1.00$ (pentagon or star);
+        \item 4 corners for the channel multiplier of $0.75$ (square or diamond);
+        \item 3 corners for the channel multiplier of $0.50$ (triangle-up or triangle-down);
+        \item ``no corners'' foo the channel multiplier of $0.25$ (circle or octagon).
+      \end{itemize}
       }
+  \end{itemize}
+\end{itemize}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%CK_INTERACTIVE_START
+Black crosses mark points lying on a Pareto-optimal frontier. 
+%
+From any point on the frontier, to increase the accuracy (move up), one must
+increase the execution time (move to the right); alternatively, to decrease the
+execution time (move to the left), one must decrease the accuracy (move down).
 
-%CK_ABSTRACT={paper_abstract.tex}
+For example, the fastest model (with the input resolution of $128$ and the
+channel multipler of $0.25$) takes $10$~ms per input image, but only achieves
+the top 1 accuracy of $40.7\%$. 
+%
+The most accurate model (with the input resolution of $224$ and the channel
+multiplier of $1.00$) takes under $50$~ms per image, with the top 1 accuracy of
+$70.5\%$.
+%
+We note that GEMM-based convolution (in v18.03) is faster than the new direct
+convolution kernel (``dv/dt'') only for the most accurate model.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction} % Has to be here (for interactive report!)
-\label{introduction} % Has to be here (for interactive report!)
+\subsection{Top 1 accuracy over 50,000 images}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Acknowledgments}
-\label{sec:ack}
+Given long exploration times for the 16 MobileNets variants over the 50,000
+image set, we use the same accuracy for all the ArmCL variants as measured
+using v18.03.
 
-%CK_IMG={http://cknowledge.org/images/logo-dividiti2.png ; http://dividiti.com}
-%CK_IMG={http://cknowledge.org/images/CTuning_foundation_logo2.png ; http://cTuning.org}
+As Table~\ref{tab:50000} shows, while this accuracy is similar to the accuracy
+measured from a TensorFlow implementation, it is not exactly the same, even
+though both implementations use the same set of weights and
+preprocessing of input images.
 
-%CK_TEX={appendix1.tex}
+Moreover, the measured accuracy is up to $0.8\%$ lower than the accuracy
+claimed for the same set of weights.
+%
+We speculate that this discrepancy is due to a difference in preprocessing of
+input images.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%-------------------------------------------------------------------------------
+% Figure 2.
+%-------------------------------------------------------------------------------
+\begin{figure*}[htbp]
+  \centering
+  \includegraphics[width=0.95\textwidth]{figures/hikey-960-accuracy_top1_-50000-dv_dt__18_03__18_01__17_12__tf.pdf}
+  \caption{Execution time vs.\ top 1 accuracy on 50,000 images (uniform accuracy across all the ArmCL variants).}
+  \label{fig:50000}
+\end{figure*}
 
-\bibliographystyle{abbrv}
+%-------------------------------------------------------------------------------
+% Table 2.
+%-------------------------------------------------------------------------------
+\begin{table}[htbp]
+  \centering
+  \input{tables/accuracy_top1-50000.tex}
+  \caption{Top 1 accuracy on 50,000 images.
+The data in the last column was taken from an older version of the MobileNets page on GitHub: \url{https://github.com/tensorflow/models/blob/1630da3434974e9ad5a0b6d887ac716a97ce03d3/research/slim/nets/mobilenet_v1.md} (which presumably corresponds to the set of weights released on 14 June 2017).}
+  \label{tab:50000}
+\end{table}
+
+%-------------------------------------------------------------------------------
+\subsection{Top 1 accuracy over 500 images}
+%-------------------------------------------------------------------------------
+
+Consider the top row of Table~\ref{tab:50000}.
+%
+A discrepancy of $0.0002$ (equivalent to 1 image out of 50,000) measured between ArmCL and TensorFlow might not sound much.
+%
+A closer investigation over the first 500 images in this data set, however,
+revealed 3 cases in which the ArmCL implementation classified images
+differently from the TensorFlow one.
+%
+In all these cases, TensorFlow predicted the top class correctly, while ArmCL predicted
+the correct class as the second most likely.
+%
+From the overall discrepancy of $0.0002$, it follows that there existed cases
+where ArmCL predicted the top class correctly, while TensorFlow did not.
+%
+Such cases could be of great interest to numerical analysts.
+%
+
+\begin{table*}[htb]
+  \centering
+  \begin{tabular}{l|l}
+  \toprule
+  {\bf ArmCL predictions} & {\bf TensorFlow predictions} \\
+  \midrule
+  \midrule
+  \multicolumn{2}{l}{ILSVRC2012\_val\_00000060.JPEG - (588) n03482405 hamper} \\
+  \midrule
+  0.45 - (492) n03014705 chest                              &  0.47 - (588) n03482405 hamper                              \\
+  0.45 - (588) n03482405 hamper                             &  0.43 - (492) n03014705 chest                               \\ 
+  0.02 - (626) n03666591 lighter, light, igniter, ignitor   &  0.02 - (626) n03666591 lighter, light, igniter, ignitor    \\
+%  0.01 - (526) n03179701 desk                               &  0.01 - (526) n03179701 desk                                \\
+%  0.01 - (681) n03832673 notebook, notebook computer        &  0.01 - (681) n03832673 notebook, notebook computer         \\
+  \midrule
+  \multicolumn{2}{l}{ILSVRC2012\_val\_00000302.JPEG - (469) n02939185 caldron, cauldron} \\
+  \midrule
+  0.48 - (926) n07590611 hot pot, hotpot                    &  0.47 - (469) n02939185 caldron, cauldron                   \\
+  0.47 - (469) n02939185 caldron, cauldron                  &  0.47 - (926) n07590611 hot pot, hotpot                     \\
+  0.02 - (925) n07584110 consomme                           &  0.02 - (925) n07584110 consomme                            \\
+%  0.01 - (996) n13052670 hen-of-the-woods                   &  0.01 - (996) n13052670 hen-of-the-woods                    \\
+%  0.01 - (809) n04263257 soup bowl                          &  0.01 - (809) n04263257 soup bowl                           \\
+  \midrule
+  \multicolumn{2}{l}{ILSVRC2012\_val\_00000313.JPEG - (979) n09468604 valley, vale} \\
+  \midrule
+  0.18 - (984) n11879895 rapeseed                           &  0.17 - (979) n09468604 valley, vale                        \\
+  0.17 - (979) n09468604 valley, vale                       &  0.17 - (984) n11879895 rapeseed                            \\
+  0.11 - (978) n09428293 seashore, coast, seacoast          &  0.12 - (978) n09428293 seashore, coast, seacoast           \\
+%  0.09 - (525) n03160309 dam, dike, dyke                    &  0.09 - (525) n03160309 dam, dike, dyke                     \\
+%  0.07 - (483) n02980441 castle                             &  0.07 - (975) n09332890 lakeside, lakeshore                 \\
+  \bottomrule
+  \end{tabular}
+
+  \caption{Image classification differences between ArmCL~v18.03 and
+TensorFlow~v1.7 over the first 500 images in the ImageNet validation set. For
+each image, the correct label is shown against its file name; below, the top 3
+predictions according to ArmCL (left column) and TensorFlow (right column) are
+shown together with their probabilities.}
+
+  \label{tab:500}
+\end{table*}
+
+Having observed the differences between ArmCL and TensorFlow, we measured the
+accuracy over the same 500 images for all the ArmCL variants on HiKey
+(Figure~\ref{fig:500:hikey}) and Firefly (Figure~\ref{fig:500:firefly}).
+%
+On both platforms, the results were identical to v18.03, except for v17.12.
+%
+With v17.12, only the models with the input resolution of $128$ produced the same
+results. For the other input resolutions, the differences ranged from $5.8\%$
+to $58.6\%$ on HiKey and from $7.2\%$ to $59.4\%$ on Firefly, with differences
+also between the GEMM-based and direct convolution approaches.
+%
+This clearly indicated a platform-independent issue in v17.12.
+%
+Had it not got fixed in v18.01, this information could have been useful for
+debugging.
+%
+
+\begin{figure*}[tp]
+  \centering
+   \subfloat[HiKey.\label{fig:500:hikey}]{%
+    \includegraphics[width=0.95\textwidth]{figures/hikey-960-accuracy_top1-500-dv_dt__18_03__18_01__17_12__tf.pdf}
+  }
+  \hfill
+  \subfloat[Firefly.\label{fig:500:firefly}]{%
+    \includegraphics[width=0.95\textwidth]{figures/firefly-accuracy_top1-500-18_03__18_01__17_12__tf.pdf}
+  }
+  \caption{Execution time vs.\ top 1 accuracy on 500 images.\label{fig:500}}
+\end{figure*}
+
+Finally, we observed differences between the platforms. 
+%
+For example, the model with the input resolution of $128$ and the channel
+multiplier of $0.50$ scored $53.6\%$ with ArmCL and TensorFlow on HiKey but
+$56.6\%$ with ArmCL and $55.6\%$ with TensorFlow on Firefly.
+
+%-------------------------------------------------------------------------------
+\subsection{Execution time on HiKey and Firefly}
+%-------------------------------------------------------------------------------
+
+Figure~\ref{fig:500} can also be studied to compare the experimental platforms.
+%
+On purpose, the X axis extends to 75~ms in Figure~\ref{fig:500:hikey} and to
+150~ms in Figure~\ref{fig:500:firefly}, since HiKey has twice as many GPU cores
+and ``big'' CPU cores as Firefly (see Table~\ref{tab:platforms}).
+%
+
+On the one hand, HiKey tends to be less efficient per GPU core than Firefly for
+the models with the channel multipliers of $0.25$ and $0.50$. 
+%
+For example, the least accurate model takes 10~ms on both platforms.
+%
+This is likely due to the limited parallelism of the workload.
+
+On the other hand, HiKey is up to $50\%$ more efficient per GPU core (3 times
+faster) than Firefly for the models with the channel multiplier of $1.00$.
+%
+This is likely due to the innate architectural differences between the newer
+Bifrost and older Midgard GPU architectures.
+
+%===============================================================================
+\section{Conclusion and future work}
+%===============================================================================
+
+We have retargeted a customizable and portable Collective Knowledge autotuning
+workflow from~\cite{cm:29db2248aba45e59:c4b24bff57f4ad07} to study the performance
+and accuracy trade-offs of the MobileNets family across many combinations of
+parameters, libraries, data sets and platforms. 
+%
+For example, by sacrificing $7\%$ of the accuracy, the execution time of the
+most accurate model can be reduced by 2 times on HiKey and by 3 times on
+Firefly; even more dramatically, by sacrificing $30\%$ of the accuracy, the
+execution time can be reduced by 5 times on HiKey and by 14 times on Firefly.
+
+Our study highlights the challenge of maintaining the accuracy when deploying
+CNN models across diverse platforms.
+%
+We have observed up to $3\%$ differences when using the same set of 32-bit
+floating point weights across libraries and platforms.
+%
+This challenge will only intensify when considering aggressive optimization
+techniques such as weights pruning and quantization.
+
+The presented Collective Knowledge workflow can be extended to support:
+\begin{itemize}
+
+  \item further autotuning choices such as the batch size, processor frequency, numerical precision, etc.;
+
+  \item further autotuning objectives such as power consumption, memory usage and hardware cost;
+
+  \item other models for resource-constrained platforms such as MobileNets-v2~\cite{Sandler:MobileNets-v2}, SqueezeNet~\cite{Iandola:SqueezeNet}, etc.;
+
+  \item emerging hardware platforms with neural network acceleration such as Linaro's HiKey970, Rock960 and Ultra96 development boards;\footnote{\url{https://www.96boards.ai/}}
+
+  \item Google's Android Neural Networks API\footnote{\url{https://developer.android.com/ndk/guides/neuralnetworks}} and TensorFlow Lite;\footnote{\url{https://www.tensorflow.org/mobile/tflite}}
+
+  \item vendor-specific frameworks such as Arm's Neural Network SDK,\footnote{\url{https://developer.arm.com/products/processors/machine-learning/arm-nn}} Qualcomm's Snapdragon Neural Processing Engine,\footnote{\url{https://developer.qualcomm.com/software/qualcomm-neural-processing-sdk}} Huawei's HiAi Computing Platform,\footnote{\url{http://developer.huawei.com/consumer/en/service/HiAI.html}} etc.
+
+\end{itemize}
+
+%===============================================================================
+% Acknowledgements.
+%===============================================================================
+\begin{acks}
+
+We thank Anthony Barbier, Georgios Pinitas, Gian Marco Iodice, Peter Horsman
+and Jim Chaney from Arm, and Daniil Efremov and Dmitry Savenko from Xored for
+collaboration on optimizing deep learning operators for the Arm Bifrost GPU
+architecture.
+
+\end{acks}
+%===============================================================================
+
+%===============================================================================
+% Bibliography.
+%===============================================================================
+\bibliographystyle{ACM-Reference-Format}
 \bibliography{paper}
+%===============================================================================
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%===============================================================================
+% Appendix
+%===============================================================================
 \appendix
-
 \clearpage
@@
 \pagebreak
-
-\input{appendix1.tex}
+\input{paper_appendix.tex}
+%===============================================================================
 

### 2018-05-31 dissemination.publication/08da9685582866a0/paper_abstract.tex
ReadMe clean up and paper sources

We present a customizable Collective Knowledge workflow with
an integrated scoreboard to automate multi-objective benchmarking,
exploration and co-design of diverse machine learning models,
frameworks, libraries and platforms.
%
We demonstrate how it can help to automatically find 
the most efficient stack for image classification 
on a Pareto frontier of accuracy, speed and size 
across MobileNets, TensorFlow, ArmCL OpenCL libraries,
and Arm Mali GPUs.
%
All artifacts, workflows and results from this paper
are shared as open-source, reproducible and reusable components
with a common JSON API for further validation, comparison
and improvement by the community.

These customizable and portable workflows can help enhance 
existing benchmarks such as MLPerf with plug\&play components 
and a live dashboard for a collaborative, reproducible and 
fair comparison of novel techniques, frameworks and platforms.
%
Such approach can help to guide further software and hardware improvements, 
automate Artifact Evaluation at conferences such as SysML, 
and accelerate technology transfer to industry.

### 2018-05-31 dissemination.publication/08da9685582866a0/paper_appendix.tex
ReadMe clean up and paper sources

%CK_APPENDIX={A}%
\onecolumn

\section{Artifact Appendix}
\label{artifact_appendix}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Abstract}

This Artifact Appendix describes experimental workflow,
artifacts and results from this paper evaluated 
during the 1st reproducible ReQuEST tournament at the ACM ASPLOS'18:

\begin{packed_itemize}
  \item {\bf Live CK workflow:} \url{https://github.com/dividiti/ck-request-asplos18-mobilenets-armcl-opencl}
  \item {\bf CK results:} \url{https://github.com/ctuning/ck-request-asplos18-results-mobilenets-armcl-opencl}
  \item {\bf Artifact DOI:} \url{https://doi.org/10.1145/3229773}
  \item {\bf ReQuEST submission and reviewing guidelines:} \url{http://cknowledge.org/request-cfp-asplos2018.html} (\cite{request-asplos18})
  \item {\bf ReQuEST goals:} \cite{cm:29db2248aba45e59:0c7348dfbadd5b95}
  \item {\bf ReQuEST workflows:} \url{https://github.com/ctuning/ck-request-asplos18-results}
  \item {\bf ReQuEST scoreboard:} \url{http://cKnowledge.org/request-results}
\end{packed_itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Description}

\subsubsection{Artifact check-list}

Details: \url{http://cTuning.org/ae/submission_extra.html}

\begin{packed_itemize}
  \item {\bf Algorithm:} image classification
  \item {\bf Program:} MobileNets using Arm Compute Library v17.12+ and TensorFlow 1.7.0+
  \item {\bf Compilation:} GCC v6+ (recommended v7+); Python 2.7+ or 3.4+
  \item {\bf Transformations:}
  \item {\bf Binary:} compiled from source on a target platform
  \item {\bf Data set:} ImageNet 2012 validation (50,000 images)
  \item {\bf Run-time environment:} Linux; OpenCL v1.2+
  \item {\bf Hardware:} Linaro HiKey960, Firefly RK3399 development boards (or similar)
  \item {\bf Run-time state:} CPU and GPU frequencies set to the maximum
  \item {\bf Execution:} 
  \item {\bf Metrics:} total execution time; top1/top5 accuracy over some (all) images from the data set
  \item {\bf Output:} classification result; execution time (throughput/latency) versus accuracy
  \item {\bf Experiments:} automated via CK command line
  \item {\bf How much disk space required (approximately)?} 4..20GB depending on library installations
  \item {\bf How much time is needed to prepare workflow (approximately)?} from 30 minutes to 1 day (if natively building TF)
  \item {\bf How much time is needed to complete experiments (approximately)?} from 30 minutes to 1 week (if validating accuracy on complete data set)
  \item {\bf Publicly available?:} Yes
  \item {\bf Code license(s)?:} BSD 3-clause
  \item {\bf CK workflow framework used?} Yes
  \item {\bf CK workflow URL:} \url{https://github.com/dividiti/ck-request-asplos18-mobilenets-armcl-opencl}
  \item {\bf CK results URL:} \url{https://github.com/ctuning/ck-request-asplos18-results-mobilenets-armcl-opencl}
\end{packed_itemize}

%-------------------------------------------------------------------------------
\subsubsection{How software can be obtained?}

\textbf{NB:} Execute commands prefixed with `\#` sign under `root` or using `sudo`.

First, install CK workflow framework:

\begin{verbatim}
# apt install python python-pip
# pip install ck
\end{verbatim}

Alternatively, you can install latest CK version in a user space from GitHub:
\begin{verbatim}
$ git clone http://github.com/ctuning/ck
$ export PATH=$PWD/ck/bin:$PATH
$ export PYTHONPATH=$PWD/ck:$PYTHONPATH
\end{verbatim}

\noindent Then, install CK repositories:
\begin{verbatim}
$ ck pull repo --url=https://github.com/dividiti/ck-request-asplos18-mobilenets-armcl-opencl
$ ck pull repo:ck-tensorflow
\end{verbatim}

%-------------------------------------------------------------------------------
\subsubsection{Hardware dependencies}

The new direct convolution kernel optimized for the Arm Mali Bifrost GPU
architecture can be evaluated on a Mali-G71 GPU (e.g.\ found in the HiSilicon
Kirin 960 chip) or Mali-G72 GPU (e.g.\ found in the HiSilicon Kirin 970 chip).
%
The workflow, however, can also be tested on any Arm Mali GPU with the Arm Mali
Midgard GPU architecture (e.g.\ Mali-T880 found in the Rockchip RK3399 chip).

%-------------------------------------------------------------------------------
\subsubsection{Software dependencies}

Software dependencies for CK workflows are automatically installed and rebuilt 
via shared CK packages: \url{https://github.com/ctuning/ck/wiki/Shared-packages}.

However, they may still require some native packages:

\paragraph{ArmCL}

\begin{verbatim}
# apt install libblas-dev liblapack-dev libatlas-base-dev
# apt install python-numpy python-scipy
# pip install pillow
\end{verbatim}

\paragraph{TensorFlow}

\begin{verbatim}
# apt install liblapack-dev libatlas-dev
# pip install enum34 mock pillow wheel absl-py scipy
$ ck install ck-env:package:jdk-8u131-universal
$ ck install ck-env:package:tool-bazel-0.11.1-linux
\end{verbatim}

%-------------------------------------------------------------------------------
\subsubsection{Data sets}

\begin{verbatim}
$ ck install package:imagenet-2012-val-min-resized
$ ck install package:imagenet-2012-aux
\end{verbatim}

\paragraph{ArmCL}

\begin{verbatim}
$ ck install package --tags=mobilenet-v1-all,npy
\end{verbatim}

\paragraph{TensorFlow}

\begin{verbatim}
$ ck install package \
  --tags=mobilenet-v1-all,tensorflowmodel,2017_06_14 
\end{verbatim}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Installation}

\paragraph{ArmCL}

\begin{verbatim}
$ ck install package:lib-armcl-opencl-request
$ ck install package:lib-armcl-opencl-18.03 \
  --env.USE_GRAPH=ON --env.USE_NEON=ON
\end{verbatim}

\paragraph{TensorFlow}

\begin{verbatim}
$ ck install package:lib-tensorflow-1.7.0-src-cpu \
  --env.CK_HOST_CPU_NUMBER_OF_PROCESSORS=1
\end{verbatim}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Experiment workflow}

\paragraph{ArmCL}

\begin{verbatim}
$ cd `ck find script:mobilenets-armcl-opencl`
$ python benchmark.py [--repetitions=10]
$ python benchmark.py --accuracy
\end{verbatim}

\paragraph{TensorFlow}

\begin{verbatim}
$ cd `ck find script:mobilenets-tensorflow`
$ python benchmark.py [--repetitions=10]
$ python benchmark.py --accuracy
\end{verbatim}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evaluation and expected result}

\begin{verbatim}
$ ls `ck find jnotebook:mobilenets-armcl-opencl`
analysis.ipynb
\end{verbatim}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Notes}

We suggest to check the ReadME from the live CK workflow 
for the latest installation and usage instructions:

\url{https://github.com/dividiti/ck-request-asplos18-mobilenets-armcl-opencl} .

### 2018-05-31 dissemination.publication/08da9685582866a0/paper.tex
clean up

@@
 %Conference
-\acmConference[ReQuEST at ASPLOS'18]{1st ACM SIGARCH Reproducible Quality-Efficient Systems Tournament and Workshop to Co-design Pareto-efficient Deep Learning}{March 2018}{Williamsburg, VA, USA}
+\acmConference[ReQuEST at ASPLOS'18]{1st ACM SIGARCH Reproducible Quality-Efficient Systems Tournament to Co-design Pareto-efficient Deep Learning}{March 2018}{Williamsburg, VA, USA}
 \acmYear{2018}

### 2018-05-31 dissemination.publication/08da9685582866a0/paper.tex
clean up

@@
 %Conference
-\acmConference[ReQuEST at ASPLOS'18]{1st ACM SIGARCH Reproducible Quality-Efficient Systems Tournament to Co-design Pareto-efficient Deep Learning}{March 2018}{Williamsburg, VA, USA}
+\acmConference[ReQuEST at ASPLOS'18]{1st ACM Reproducible Quality-Efficient Systems Tournament on Co-designing Pareto-efficient Deep Learning}{March 2018}{Williamsburg, VA, USA}
 \acmYear{2018}

### 2018-06-01 dissemination.publication/08da9685582866a0/paper_appendix.tex
clean up

@@
 \label{artifact_appendix}
+
+Submission and reviewing methodology: \\
+{\em http://cTuning.org/ae/submission-20171101.html}
 
@@
 \begin{packed_itemize}
-  \item {\bf Live CK workflow:} \url{https://github.com/dividiti/ck-request-asplos18-mobilenets-armcl-opencl}
+  \item {\bf Latest CK workflow:} \url{https://github.com/dividiti/ck-request-asplos18-mobilenets-armcl-opencl}
   \item {\bf CK results:} \url{https://github.com/ctuning/ck-request-asplos18-results-mobilenets-armcl-opencl}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Description}
-
-\subsubsection{Artifact check-list}
+\subsection{Artifact check-list}
 
@@
 %-------------------------------------------------------------------------------
-\subsubsection{How software can be obtained?}
+\subsection{Description}
+
+\subsubsection{How to obtain}
 

### 2018-06-11 dissemination.publication/08da9685582866a0/paper_appendix.tex
improved meta for ACM DL proceedings
added instructions how to use CK snapshot from ACM DL

@@
 
-Alternatively, you can install latest CK version in a user space from GitHub:
+Alternatively, you can install the latest CK version in a user space from GitHub:
 \begin{verbatim}
@@
 $ ck pull repo --url=https://github.com/dividiti/ck-request-asplos18-mobilenets-armcl-opencl
-$ ck pull repo:ck-tensorflow
 \end{verbatim}
+
+\subsubsection{Install this CK workflow from the ACM Digital Library snapshot}
+
+It is possible to install and test the snapshot of this workflow 
+from the ACM Digital Library without interfering with your current CK installation.
+Download related file "request-asplos18-artifact-?-ck-workflow.zip"
+to a temporary directory, unzip it and then execute the following commands:
+
+\begin{verbatim}
+$ . ./prepare_virtual_ck.sh
+$ . ./start_virtual_ck.sh
+\end{verbatim}
+
+All CK repositories will be installed in your current directory.
+You can now proceed with further evaluation as described below.
 

### 2018-06-12 dissemination.publication/08da9685582866a0/paper_appendix.tex
Update appendix.

--- 2018-06-01 dissemination.publication/08da9685582866a0/paper_appendix.tex
@@
   \item {\bf How much disk space required (approximately)?} 4..20GB depending on library installations
-  \item {\bf How much time is needed to prepare workflow (approximately)?} from 30 minutes to 1 day (if natively building TF)
-  \item {\bf How much time is needed to complete experiments (approximately)?} from 30 minutes to 1 week (if validating accuracy on complete data set)
+  \item {\bf How much time is needed to prepare workflow (approximately)?} from 30 minutes to 1 day (if natively building TensorFlow)
+  \item {\bf How much time is needed to complete experiments (approximately)?} from 30 minutes to 1 week (if validating accuracy on the full ImageNet validation data set of 50,000 images)
   \item {\bf Publicly available?:} Yes
@@
 
-\textbf{NB:} Execute commands prefixed with `\#` sign under `root` or using `sudo`.
+\textbf{NB:} Execute commands prefixed with `\#' sign under the `root' account or with `sudo'.
 
-First, install CK workflow framework:
+First, install the Collective Knowledge framework (CK):
 
@@
 
-Alternatively, you can install latest CK version in a user space from GitHub:
+Alternatively, you can install the latest CK version from GitHub in the user space:
 \begin{verbatim}
@@
 
-\noindent Then, install CK repositories:
+\noindent Then, install the required CK repositories:
 \begin{verbatim}
 $ ck pull repo --url=https://github.com/dividiti/ck-request-asplos18-mobilenets-armcl-opencl
-$ ck pull repo:ck-tensorflow
 \end{verbatim}
+
+\subsubsection{Install this CK workflow from the ACM Digital Library snapshot}
+
+You can install and test a snapshot of this workflow 
+from the ACM Digital Library without interfering with your current CK installation.
+Download related file {\tt request-asplos18-artifact-?-ck-workflow.zip}
+to a temporary directory, unzip it and then execute the following commands:
+
+\begin{verbatim}
+$ . ./prepare_virtual_ck.sh
+$ . ./start_virtual_ck.sh
+\end{verbatim}
+
+All the required CK repositories will be installed in your current directory.
+%You can now proceed with further evaluation as described below.
 
@@
 Software dependencies for CK workflows are automatically installed and rebuilt 
-via shared CK packages: \url{https://github.com/ctuning/ck/wiki/Shared-packages}.
-
+via shared CK packages.\footnote{\url{https://github.com/ctuning/ck/wiki/Shared-packages}}
 However, they may still require some native packages:
@@
 \begin{verbatim}
-$ ck install package \
-  --tags=mobilenet-v1-all,tensorflowmodel,2017_06_14 
+$ ck install package --tags=mobilenet-v1-all,tensorflowmodel,2017_06_14 
 \end{verbatim}
@@
 $ ck install package:lib-armcl-opencl-request
-$ ck install package:lib-armcl-opencl-18.03 \
-  --env.USE_GRAPH=ON --env.USE_NEON=ON
+$ ck install package:lib-armcl-opencl-18.03 --env.USE_GRAPH=ON --env.USE_NEON=ON
 \end{verbatim}
@@
 \begin{verbatim}
-$ ck install package:lib-tensorflow-1.7.0-src-cpu \
-  --env.CK_HOST_CPU_NUMBER_OF_PROCESSORS=1
+$ ck install package:lib-tensorflow-1.7.0-src-cpu --env.CK_HOST_CPU_NUMBER_OF_PROCESSORS=1
 \end{verbatim}
@@
 
-We suggest to check the ReadME from the live CK workflow 
-for the latest installation and usage instructions:
+We recommend to check {\tt README} from the live CK workflow for the latest
+installation and usage instructions:
 
-\url{https://github.com/dividiti/ck-request-asplos18-mobilenets-armcl-opencl} .
+\url{https://github.com/dividiti/ck-request-asplos18-mobilenets-armcl-opencl}

### 2018-06-12 dissemination.publication/08da9685582866a0/paper.tex
improved meta for ACM DL proceedings
added ISBN
Clarify that the accuracy claim was made by the MobileNets authors.

@@
 % ISBN
-\acmISBN{}
+\acmISBN{978-1-4503-5923-8}
 
@@
 
-  \item The colour of a marker denotes the execution engine: TensorFlow on the CPU or the ArmCL on the GPU.
+  \item The colour of a marker denotes the execution engine: TensorFlow on the CPU or ArmCL on the GPU.
 
@@
 Moreover, the measured accuracy is up to $0.8\%$ lower than the accuracy
-claimed for the same set of weights.
+that the MobileNets authors claimed for the same set of weights.
 %

### 2018-06-12 dissemination.publication/08da9685582866a0/paper_abstract.tex
improved meta for ACM DL proceedings
Update abstract.

@@
-We present a customizable Collective Knowledge workflow with
-an integrated scoreboard to automate multi-objective benchmarking,
-exploration and co-design of diverse machine learning models,
-frameworks, libraries and platforms.
+We present a customizable Collective Knowledge workflow to study the execution
+time vs.\ accuracy trade-offs for the MobileNets CNN family.
 %
-We demonstrate how it can help to automatically find 
-the most efficient stack for image classification 
-on a Pareto frontier of accuracy, speed and size 
-across MobileNets, TensorFlow, ArmCL OpenCL libraries,
-and Arm Mali GPUs.
+We use this workflow to evaluate MobileNets on Arm Cortex CPUs using TensorFlow
+and Arm Mali GPUs using several versions of the Arm Compute Library.
 %
-All artifacts, workflows and results from this paper
-are shared as open-source, reproducible and reusable components
-with a common JSON API for further validation, comparison
-and improvement by the community.
-
-These customizable and portable workflows can help enhance 
-existing benchmarks such as MLPerf with plug\&play components 
-and a live dashboard for a collaborative, reproducible and 
-fair comparison of novel techniques, frameworks and platforms.
+Our optimizations for the Arm Bifrost GPU architecture reduce the execution
+time by 2--3 times, while lying on a Pareto-optimal frontier.
 %
-Such approach can help to guide further software and hardware improvements, 
-automate Artifact Evaluation at conferences such as SysML, 
-and accelerate technology transfer to industry.
+We also highlight the challenge of maintaining the accuracy when deploying CNN
+models across diverse platforms.
+%
+We make all the workflow components (models, programs, scripts, etc.) publicly
+available to encourage further exploration by the community.

### 2018-06-14 report/08da9685582866a0/view.sh
cleaned up not needed report

@@ -1,1 +1,0 @@
-ck browser ^
